---
title: "GerminaR 1.0"
author: "Flavio Lozano, Omar Benites, Bruno Pompelli"
date: "`r Sys.Date()`"
output: 
      rmarkdown::html_vignette:
        toc: true
        toc_depth: 4
        keep_md: true
vignette: >
  %\VignetteIndexEntry{GerminaR 1.0}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Firt we have to load the `GerminaR 1.0` package. It provides the `GerminaR` dataset that we will use throghout all the examples. 

```{r}
library(GerminaR)
dim(GerminaR)
str(GerminaR)
```

GerminaR aims to make available Germination seed indexes and graphic functions to analyze germination seed data:

* `ger_ASG`
* `ger_cumsum`
* `ger_CVG`
* `ger_GRP`
* `ger_GRS`
* `ger_GSP`
* `ger_intime`
* `ger_MGR`
* `ger_MGT`
* `ger_SDG`
* `ger_summary`
* `ger_SYN`
* `ger_UNC`
* `ger_VGT`


## Germinated Seed Number

`ger_ASG()` allow to calculate the arcsin of germination percentage for normalization.

```{r}
dt <- GerminaR
grs <- ger_GRS(evalName = "Ev", data = dt)
head(grs)
```


## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
