---
title: "GerminaR 1.0"
author: "Flavio Lozano-Isla, Omar Benites-Alfaro, Denise Garcia de Santana, Marli A. Ranal, Marcelo Francisco Pompelli"
date: "`r Sys.Date()`"
output: 
      rmarkdown::html_vignette:
        toc: true
        toc_depth: 4
        keep_md: true
vignette: >
  %\VignetteIndexEntry{GerminaR 1.0}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


The package `GerminaR` has been developed to calculate different germination indices and graphical functions to analyze punctual and accumulative germination. For calculating the indices is necessary acumulative germination data. For more details, you can read the description of each index, the seed germination dataset and analysis in the germinar's book. ([GerminaQuant](https://flavjack.github.io/GerminaQuant-usm/))


First we load the `GerminaR 1.4` package. It provides the `prosopis` dataset set that we will work throughout all the examples. 


## Data: GerminaR

The `prosopis` dataset contains information from an experiment containing information from germination experiment with *Prosopis juliflor* under different osmotic potentials and temperatures evaluated during 10 days.

```{r}
library(GerminaR)
dim(prosopis)
str(prosopis)
```


## List of the principal functions

* `GerminaQuant`
* `ger_summary`
* `ger_GRS`
* `ger_GRP`
* `ger_ASG`
* `ger_MGT`
* `ger_MGR`
* `ger_GSP`
* `ger_SYN`
* `ger_UNC`
* `ger_SDG`
* `ger_CVG`
* `ger_VGT`
* `ger_intime`
* `fplot` 

## Interactive shiny application

The function`GerminaQuant()` activates an interactive application with friendly interface for performing the different germination, statistical and graphic analysis. For activation of some function could be necessary internet connection

```{r, eval=FALSE}
GerminaQuant()
```


## Summary of Germination Variables

The function `ger_summary()`, according to the accumulative germination data, calculates eleven germination indices maintaining the values of each experimental unit and experiments factor for statistical analysis


```{r}
dfr <- prosopis
smr <- ger_summary(SeedN = "seeds", evalName = "D", data = dfr)
knitr::kable(head(smr, 10),align = "c")
```


On the other hand, you can analyze each variable independently using the following germination indexes.


## Germinated Seed Number

`ger_GRS()` allows you to calculate the number of seed germinated.


```{r}
dfr <- prosopis
grs <- ger_GRS(evalName = "D", data = dfr)
grs
```


## Germination Seed Percentage

`ger_GRP()` calculates the germination percentage related at total seed sown for experimental unit.

```{r}
dfr <- prosopis
grp <- ger_GRP(SeedN = "seeds",evalName = "D", data = dfr)
grp
```


## ArcSino of the germination

`ger_ASG()`  calculates the arc sin of germination percentage for normalization.

```{r}
dfr <- prosopis
gas <- ger_ASG(SeedN = "seeds", evalName = "D", data = dfr)
gas
```


## Mean Germination Time

`ger_MGT()` estimates the mean germination time according at the time lapse of the evaluations

```{r}
dfr <- prosopis
mgt <- ger_MGT(evalName = "D", data = dfr)
mgt
```


## Mean Germination Rate

`ger_MGR()` estimates the mean of germination rate

```{r}
dfr <- prosopis
mgr <- ger_MGR(evalName = "D", data = dfr)
mgr
```


## Germination Speed

`ger_GSP()` performs the calculation of germination speed according at the time lapse of the evaluations.

```{r}
dfr <- prosopis
gsp <- ger_GSP(evalName = "D", data = dfr)
gsp
```


## Germination Synchronization Index

`ger_SYN()` calculates germination synchronization of the germination process.

```{r}
dfr <- prosopis
syn <- ger_SYN(evalName = "D", data = dfr)
syn
```

## Germination Uncertainty

`ger_UNC()` measures the germination uncertainty into the germination process.


```{r}
dfr <- prosopis
unc <- ger_UNC(evalName = "D", data = dfr)
unc
```


## Standard deviation of the Mean Germination Time

`ger_SDG()` estimates the standard deviation of the mean germination time.

```{r}
dfr <- prosopis
sdg <- ger_SDG(evalName = "D", data = dfr)
sdg
```


## Coefficient of Variance of the Mean Germination Time

`ger_CVG()`  Coefficient of Variance of the Mean Germination Time

```{r}
dfr <- prosopis
cvg <- ger_CVG(evalName = "D", data = dfr)
cvg
```


## Variance of the Mean Germination Time

`ger_VGT()` compute the variance of the mean during germination time.

```{r}
dfr <- prosopis
vgt <- ger_VGT(evalName = "D", data = dfr)
vgt
```

## Accumulative germination

`ger_intime()` Allow to calculate the accumulative germination

```{r}
dfr <- prosopis
grt <- ger_intime(Factor = "nacl", SeedN = "seeds", evalName = "D", method = "percentage", data = dfr)
head(grt, 10)
```


## Plot function


`fplot()` is generic plot function optimized for publication graphs

```{r,  warning=FALSE }
dfr <- prosopis
grt <- ger_intime(Factor = "nacl", SeedN = "seeds", evalName = "D", method = "percentage", data = dfr)

fplot(data = grt, type = "line",
      x = "evaluation",
      y = "mean",
      z = "nacl",
      ylab = "Germination ('%')",
      xlab = "days", lgl = "NaCl (mM)",
      lgd = "top", color = F)

```




