---
title: "GerminaR 1.0"
author: "Flavio Lozano, Omar Benites, Bruno Pompelli"
date: "`r Sys.Date()`"
output: 
      rmarkdown::html_vignette:
        toc: true
        toc_depth: 4
        keep_md: true
vignette: >
  %\VignetteIndexEntry{GerminaR 1.0}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Firt we have to load the `GerminaR 1.0` package. It provides the `GerminaR` dataset that we will use throghout all the examples. 


## Data: GerminaR

The `GerminaR` dataset contains information from a experiremnt with 6 genotypes Jatropha curcas under 3 levels of salinity stress evaluated during 25 days.

```{r}
library(GerminaR)
dim(GerminaR)
str(GerminaR)
```

GerminaR aims to make available Germination seed indexes and graphic functions to analyze germination seed data:

* `ger_ASG`
* `ger_CVG`
* `ger_GRP`
* `ger_GRS`
* `ger_GSP`
* `ger_MGR`
* `ger_MGT`
* `ger_SDG`
* `ger_SYN`
* `ger_UNC`
* `ger_VGT`
* `ger_cumsum`
* `ger_summary`
* `ger_intime`

## Germinated Seed Number

`ger_ASG()`  Calculates the arcsin of germination percentage for normalization.

```{r}
dt <- GerminaR
grs <- ger_GRS(evalName = "Ev", data = dt)
grs
```


## Coefficient of Variance of the Mean Germination Time

`ger_CVG()`  Coefficient of Variance of the Mean Germination Time

```{r}
dt <- GerminaR
cvg <- ger_CVG(evalName = "Ev", data = dt)
cvg
```

## Germination Seed Percentage

`ger_GRP()` Calculate the germination percentage related at total seed sown for experimental unit.

```{r}
dt <- GerminaR
grp <- ger_GRP(SeedN = "NSeeds",evalName = "Ev", data = dt)
grp
```


## Germinated Seed Number

`ger_GRS()` allows you to calculate the number of seed germinated.


```{r}
dt <- GerminaR
grp <- ger_GRP(SeedN = "NSeeds",evalName = "Ev", data = dt)
grp
```


## Germination Speed

`ger_GSP()` performs the calculation of germination speed according at the time lapse of the evaluations.

```{r}
dt <- GerminaR
gsp <- ger_GSP(evalName = "Ev", data = dt)
gsp
```


## Mean Germination Rate

`ger_MGR()` measures the mean of germination rate

```{r}
dt <- GerminaR
mgr <- ger_MGR(evalName = "Ev", data = dt)
mgr
```


## Mean Germination Time

`ger_MGT()` the mean germination time according at the time lapse of the evaluations

```{r}
dt <- GerminaR
mgt <- ger_MGT(evalName = "Ev", data = dt)
mgt
```

## Standard deviation of the Mean Germination Time

`ger_SDG()` estimates the standard deviation of the mean germination time.

```{r}
dt <- GerminaR
sdg <- ger_SDG(evalName = "Ev", data = dt)
sdg
```


## Germination Synchronization Index

`ger_SYN()` calculates germination synchronization of the germination process.

```{r}
dt <- GerminaR
syn <- ger_SYN(evalName = "Ev", data = dt)
syn
```

## Germination Uncertainty

`ger_UNC()` measures the germination uncertainty into the germination process.


```{r}
dt <- GerminaR
unc <- ger_UNC(evalName = "Ev", data = dt)
unc
```


## Variance of the Mean Germination Time

`ger_VGT()` compute the cvariance of the mean during germination time.

```{r}
dt <- GerminaR
vgt <- ger_VGT(evalName = "Ev", data = dt)
vgt
```

## Summary of Germination Variables

`ger_summary()` summarizes germination variables for each experimental unit.  

```{r}
dt <- GerminaR
smr <- ger_summary(SeedN = "NSeeds", evalName = "Ev", data = dt)
knitr::kable(head(smr, 10),align = "c")
```




