---
title: "GerminaR 1.0"
author: "Flavio Lozano-Isla, Omar Benites, Marcelo Francisco Pompelli"
date: "`r Sys.Date()`"
output: 
      rmarkdown::html_vignette:
        toc: true
        toc_depth: 4
        keep_md: true
vignette: >
  %\VignetteIndexEntry{GerminaR 1.0}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


The package `GerminaR` was develop to calculate different germination indexes and graphic functions to analyze punctual and accumulative germination. For calculate the indices in necessary acumulative germination data, you can read the description of each index and the data collect and analysis in the uses manual ([GerminaQuant](https://flavjack.github.io/GermBook/))


First we have to load the `GerminaR 1.0` package. It provides the `GerminaR` data set that we will use throughout all the examples. 


## Data: GerminaR

The `GerminaR` data set contains information from a experiment with 6 genotypes *Jatropha curcas* under 3 levels of salinity stress evaluated during 25 days.

```{r}
library(GerminaR)
dim(GerminaR)
str(GerminaR)
```


## List of the principal functions

* `runGerminaQuant`
* `ger_summary`
* `ger_GRS`
* `ger_GRP`
* `ger_ASG`
* `ger_MGT`
* `ger_MGR`
* `ger_GSP`
* `ger_SYN`
* `ger_UNC`
* `ger_SDG`
* `ger_CVG`
* `ger_VGT`
* `ger_intime`
* `fplot` 

## Interactive application

The function`runGerminaQuant()` activate the interactive application with friendly interface for perform the different germination, statistical and graphic analysis. For activation of some function could be necessary internet connection

```{r, eval=FALSE}
runGerminaQuant()
```


## Summary of Germination Variables

The function `ger_summary()` according to the accumulative germination data will calculate eleven germination indices maintaining the values of each experimental unit and experiments factor for statistical analysis


```{r}
dt <- GerminaR
smr <- ger_summary(SeedN = "NSeeds", evalName = "Ev", data = dt)
knitr::kable(head(smr, 10),align = "c")
```


You can analyze each variable independently


## Germinated Seed Number

`ger_GRS()` allows you to calculate the number of seed germinated.


```{r}
dt <- GerminaR
grs <- ger_GRS(evalName = "Ev", data = dt)
grs
```


## Germination Seed Percentage

`ger_GRP()` Calculate the germination percentage related at total seed sown for experimental unit.

```{r}
dt <- GerminaR
grp <- ger_GRP(SeedN = "NSeeds",evalName = "Ev", data = dt)
grp
```


## ArcSino of the germination

`ger_ASG()`  Calculates the arc sin of germination percentage for normalization.

```{r}
dt <- GerminaR
gas <- ger_ASG(SeedN = "NSeeds", evalName = "Ev", data = dt)
gas
```


## Mean Germination Time

`ger_MGT()` the mean germination time according at the time lapse of the evaluations

```{r}
dt <- GerminaR
mgt <- ger_MGT(evalName = "Ev", data = dt)
mgt
```


## Mean Germination Rate

`ger_MGR()` Measures the mean of germination rate

```{r}
dt <- GerminaR
mgr <- ger_MGR(evalName = "Ev", data = dt)
mgr
```


## Germination Speed

`ger_GSP()` performs the calculation of germination speed according at the time lapse of the evaluations.

```{r}
dt <- GerminaR
gsp <- ger_GSP(evalName = "Ev", data = dt)
gsp
```


## Germination Synchronization Index

`ger_SYN()` calculates germination synchronization of the germination process.

```{r}
dt <- GerminaR
syn <- ger_SYN(evalName = "Ev", data = dt)
syn
```

## Germination Uncertainty

`ger_UNC()` measures the germination uncertainty into the germination process.


```{r}
dt <- GerminaR
unc <- ger_UNC(evalName = "Ev", data = dt)
unc
```


## Standard deviation of the Mean Germination Time

`ger_SDG()` estimates the standard deviation of the mean germination time.

```{r}
dt <- GerminaR
sdg <- ger_SDG(evalName = "Ev", data = dt)
sdg
```


## Coefficient of Variance of the Mean Germination Time

`ger_CVG()`  Coefficient of Variance of the Mean Germination Time

```{r}
dt <- GerminaR
cvg <- ger_CVG(evalName = "Ev", data = dt)
cvg
```


## Variance of the Mean Germination Time

`ger_VGT()` compute the variance of the mean during germination time.

```{r}
dt <- GerminaR
vgt <- ger_VGT(evalName = "Ev", data = dt)
vgt
```

## Accumulative germination

`ger_intime()` Allow to calculate the accumulative germination

```{r}
dt <- GerminaR
grt <- ger_intime(Factor = "Salt", SeedN = "NSeeds", evalName = "Ev", method = "percentage", data = GerminaR)
```


## Plot fuction


`fplot()` is generic plot function optimized for publication graphs

```{r}
dt <- GerminaR
grt <- ger_intime(Factor = "Salt", SeedN = "NSeeds", evalName = "Ev", method = "percentage", data = GerminaR)

fplot(data = grt, type = "line", 
      x = evaluation, 
      y = mean,
      z = Salt, 
      ylab = "Germination ('%')", 
      xlab = "days", lgl = "NaCl (mM)", 
      lgd = "top", 
      lmt = c(0,100), brk = 0:100*10)

```









